---
title: "Day 1:Descriptive Stats and Visualizations"
---

# May 22 9-1:30

Welcome

[Introduction](./Teaching_Introductory_Statistics_with_R_Day1_Opening.pdf){target="_blank"}

[Descriptive Statistics](./descriptive_statistics.html){target="_blank"}

-   [Activity 1 with Descriptive Statistics and births14](./Activity_1_Descriptive_Stats/Activity_1.txt)

Break?

[Numeric Data Histograms and Boxplots](./histograms.html){target="_blank"}

-   [Activity 2 with Boxplots and births14](./Activity_2_Boxplots/Boxplots.txt)

Break

[Categorical Data Scatter Plots and Correlations](./Activity_3_Categorical_Vars/SLIDES_Day1-Categorial-Data_Correlation.pdf)

::: download_btn
```{r}
#| echo: false

library(downloadthis)

download_file(
  path = "./Activity_3_Categorical_Vars/Notebook_WSDay1_Categorical_Data_ScatterPlots_Correlation.Rmd",
  output_name = "Notebook Categorical Data Scatter Plots and Correlation",
  button_label = "Download data",
  button_type = c("default"),
  has_icon = TRUE,
  icon = "fa fa-save",
  self_contained = FALSE,

)
```
:::

-   [Notebook Categorical Data Scatter Plots and Correlation](./Activity_3_Categorical_Vars/Notebook_WSDay1_Categorical_Data_ScatterPlots_Correlation.Rmd)

Lunch

-   [Activity 3 Lab on Categorical Data Scatter Plots and Correlation](./Activity_3_Categorical_Vars/LAB_WSDay1_Categorical_Data_Scatterplots_Correlation.Rmd)

------------------------------------------------------------------------

*Solutions*


```{r include=FALSE,echo=FALSE}

 
# [Activity 1](./Activity_1_Descriptive_Stats/Solutions_Activity_1.html)
# [Activity 2](./Activity_2_Boxplots/Activity_2_Boxplots_Solutions.html)
# [Activity 3](./Activity_3_Categorical_Vars/LAB_WSDay1_SOLUTIONS_Categorical-Data_Scatterplots_Correlation.pdf)
```




