---
title: "Histograms and Boxplots"
author: "Schwab"
format: revealjs
---

```{r setup}
knitr::opts_chunk$set(include=TRUE)
library(mosaic)
library(openintro)

```

## Histograms and Boxplots

Let's consider the `county` data frame.

```{r view}
#Add variable types. 
county
```

#Add names(county) to county. Size of df. mention dim()

## A simple histogram

Map the unemployment rate for the counties in the US in 2019.

```{r one-variable}
gf_histogram(~unemployment_rate,data = county)
```

## Function arguments

Every function in R can take a lot of arguments. Let's type `?gf_histogram` to see the arguments for that function.

|                  |              |           |                     |
|------------------|--------------|-----------|---------------------|
| object = NULL,   | binwidth,    | linetype, | subtitle,           |
| gformula = NULL, | alpha = 0.5, | size,     | caption,            |
| data = NULL,     | color,       | xlab,     | geom = "bar",       |
| ...,             | fill,        | ylab,     | stat = "bin",       |
| bins = 25,       | group,       | title,    | position = "stack", |

## What do these do?

Start with the single variable histogram: `gf_histogram(~unemployment_rate,data = county,...)`

::: incremental
1.  Edit the `bins` or `binwidth`, which get priority?

2.  Edit `colors` and `fill`. Which tints what? (Hint colors are strings, use quotes) [Here's a list of colors](http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf)

3.  Add a title and caption. Remove the label from the x-axis add a good one to the y.

4.  What the heck do size, linetype and group do?
:::

## Here's a graph that I made

```{r my-gfhist}
gf_histogram(~unemployment_rate,data=county,bins=10, color="black",fill="purple", xlab="",ylab="Number of unemployed", title="US Umeployment by county", caption="Data is as of 2019",linetype = 5,size=2)

```

## Show two variables

The histogram is a single variable graph by we can break up the data by grouping it.

```{r}
#Take position ="dodge" out
gf_histogram(~unemployment_rate,data=county,bins=10, fill = ~metro)
```

## Two variables (faceted):

Let's make two histograms side by side.

```{r two-variables}
gf_histogram(~unemployment_rate|~metro,data = county)
```

```{r boxplot}
gf_boxplot(~unemployment_rate,data=county, color = ~metro)
# or 
gf_boxplot(unemployment_rate~metro,data=county)
```

Some activity: Make a box plot and histogram with births14 <- make a markdown to go with this. Guided questions. 
