---
title: "Solutions Activity Descriptive Stats"
output: html_document
date: "`r Sys.Date()`"
---

These are some solutions, you should do the activity first. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#This is the setup chunk. The libraries must be loaded here. type: library(mosaic) and library(openintro) below then hit the green play button in the upper right hand corner to run the chunk.

library(mosaic)
library(openintro)

#library(tidyverse)
```

1.  We should always attempt to understand our data first.

view births14 in the chunk below. You can also use the `?` operator to learn more.

```{r understand-data}

#view(births14)
births14
?births14
```

The grey rectangles are called code chunks.

To make a new code chunk you can type three tick marks \`\`\` (the tick is above the tab key) and a curly bracket with the letter r in the middle {r}. You end a chunk with three more tick marks, like the chunks above.

2.  Make a chunk below and use `favstats()` to get an idea of the summary statistics for a baby's birthweight. You can give it a name after the r like understand-data above. No space allowed in chunk names.

```{r new-chunk}
favstats(~weight,data=births14)

```

3.  Use favstats() and a formula (use the \~) to break up the weight summary statistics by the sex of the child.

```{r two-variables}
favstats(weight~sex, data=births14)

```

4.  Challenge: Add another variable to your favstats: whether the mother was a smoker or nonsmoker. The formula will be similar to the chunk above but will include a plus sign after the second variable.

```{r three-variables}
favstats(weight~sex + habit , data=births14)
```

5.  What happens when you switch the `sex` and `habit` variables in the chunk above?

A: The summaries are the same, but is listed differently. For more examples see ?favstats()

```{r three-variables-again}
favstats(weight~habit + sex , data=births14)
```

6.  Can you use the same formulas above for the mean() and IQR() functions?

A: Yes you can!

```{r mean-iqr}
mean(weight~habit + sex , data=births14)
```
