---
title: "Confidence Interval and Hypothesis Testing"
subtitle: "Also getting numeric data into R"
format: revealjs
editor: visual
---

## Functions for Confidence Intervals

```{r setup}
#|echo:FALSE
library(mosaic)
library(openintro)
```

<br>

These are the functions for confidence intervals.

<br>

-   prop.test(...., correct =FALSE)

-   t.test()

<br>

The same functions are used for hypothesis testing.

## The Data Sets

<br>

We'll use a couple of different data sets for the different CI and hypothesis tests.

-   For a proportion we'll use the `exclusive_relationship` data set.

-   For a single mean lets use `cars93`.

-   For a difference of Means test we'll use the `Sleep` data frame (captial S).

## Proportions

If we were to run `?proptest` we'd find.

x- count of successes, length 2 vector of success and failure counts, a formula, or a character, numeric, or factor vector containing raw data.

n- sample size (successes + failures) or a data frame (for the formula interface).

conf.level- the confidence level must be between 0 and 1.

::: incremental
-   The "correct" argument is not listed.
:::

## Confidence Interval for Proportions

What is the 90% Confidence interval for the proportion of students who have been in exactly 4 relationships?

```{r tally-conditions}
#| echo: TRUE
#Assume independence
#At least 10 successes/failures
tally(~num==4, data=exclusive_relationship)
```

```{r exclusive-relationships}
#| echo: TRUE

prop.test(x= ~num == 4,data=exclusive_relationship, conf.level = 0.90, correct=FALSE)

```

## To make the CI look better

<br> You can use the \$ operator <br>

```{r dollar-sign}
#| echo: TRUE

results <- prop.test(x= ~num==4,data=exclusive_relationship, conf.level = 0.90, correct=FALSE)
results$conf.int
```

<br> or you can use the wrapper confint() <br>

```{r wrapper}
#| echo: TRUE
confint(prop.test(x= ~num==4,data=exclusive_relationship, conf.level = 0.90))
```

## You can also make a CI from a homework problem. {.smaller}

> *A store randomly samples 603 shoppers over the course of a year and finds that 142 of them made their visit because of a coupon they'd received in the mail. Construct a 95% confidence interval for the fraction of all shoppers during the year whose visit was because of a coupon they'd received in the mail.*

A sample size n=603 and 142 successes.

```{r CI-homework}
#| echo: TRUE
confint(prop.test(x=142,n=603,correct=FALSE))

```

## A Warning on Proportions

`prop.test(... correct= FALSE)` is built into mosaic and works well with problems based on the OpenIntroStats text on MyOpenMath made by Adam Gilbert. \n.

If you are using a different problem set and `prop.test()` doesn't work, you should check out `binom.test()`. \n.

`binom.test(... method="Wald")` returns the same values that a TI-83 calculator would produce.

## Proportion Hypothesis Test {.smaller}

To make a hypothesis we need two more arguments. <br>

-   p - This is the population proportion from the null hypothesis

-   alternative - c("two.sided", "less", "greater")

$H_0: p= 0.3$

$H_1: p\ne 0.3$

$\alpha=0.05$

```{r prop-hy-test}
#| echo: TRUE

prop.test(x=~num==4, p=0.3, alternative="t", data=exclusive_relationship, conf.level = 0.90, correct=FALSE)

```
