---
title: "NOTEBOOK: Workshop Day 1"
subtitle: "Categorial Variables, Scatterplots, Correlation"
author: "Your Name Here"
date: '`r Sys.Date()`'
output: 
  md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(mosaic)
library(mosaicData)
library(openintro)
library(palmerpenguins)
library(vcd)
```
# Categorical Variables  

### Contingency Tables   
The tally function counts the levels of a categorical variable.
For the *loans_full_schema* data frame, count the levels of the homeownership variable.   
```{r}

```

Count all combinations of homeownership and application_type.   
```{r}

```

Add row/column totals using margin argument.   
```{r}

```

### Bar Plots   
Create bar plot of a categorical variable with counts on the y-axis.   
```{r}

```
Proportions on the y-axis.      
```{r}

```

Percents on the y-axis.   
```{r}

```
Two Categorical variable Stacked Bar Plot.   
```{r}

```

Side-By-Side Stacked Bar Plot.   
```{r}

```

### Mosaic Plots    


# Scatterplots   
We start with the Births78 data frame in the *mosaicData* package.   
Plot births on the y-axis, date on the x-axis.    
```{r}

```
Let's add a color and label the axes and give it a title.   
```{r}

```

Color the points according to the variable wday.   
```{r}

```

Facet. 
```{r}

```

Facet with a mosaic function gf_facet_wrap().
```{r}

```

With *mtcars*, Map as many variables as we can to the plot!   
In the console, type ?mtcars to learn about the variables.  
```{r}

```

# Correlation

We can add linear and non-linear models to a scatterplot.
Let's plot mpg on the y-axis against drat, hp, wt.   
mpg ~ drat
mpg ~ hp
mpg ~ wt

Compute correlations for each of the three cases. 




